---
title: "R Notebook"
output: html_notebook
---

## Ensure Gimme is installed

```{r}
gimme_available <- require("gimme")
if(!gimme_available) {
```


```{r}
install.packages("gimme", dependencies = TRUE)
}

tidyverse_available <- require("tidyverse")
if(!tidyverse_available) {
  install.packages("tidyverse", dependencies = TRUE)
}

library(gimme)
library(dplyr)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
library(MANOVA.RM)
library(DescTools)
library(tidyr)
files <- list.files(path="../python/temp/", pattern="*.csv", full.names=TRUE, recursive=FALSE)

for (x in files) {
  path_vars <- SplitPath(x)
  data <- read.csv(file = x)
  print(path_vars$filename)
  fit <- multRM(cbind(pupil + hr + rsa + scr) ~ learners_nonlearners * decile * bin, data = data, 
              within= c("decile", "bin"), subject='participant', iter=1000, seed = 1234, para = TRUE)
  # manova(cbind(C1, C2) ~ extractants * metals, data=m_data)
  summary(fit)
}

```

